---
title: "Introduction to TransOmicsData"
author: 
    name: Carissa Chen
    affiliation: The University of Sydney
    email: carissa.chen@sydney.edu.au
output:
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{TransOmicsData: A collection of trans-omics datasets across various biological systems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

# Introduction

The TransOmicsData package contains datasets spanning various biological contexts such as in vitro embryonic and tissue-specific development in mouse and human. It covers multiple omics sequencing technologies such as RNAseq, mass spectrometry and ChIP-seq. This package was developed to provide convenient access to raw or pre-processed data for comparative trans-omics analysis.

# The TransOmicsData package

## Accessing the data

The data stored in this package can be retrieved using ExperimentHub.

```{r warning=FALSE, message=FALSE}
# if (!requireNamespace("BiocManager", quietly = TRUE))
#    install.packages("BiocManager")

# BiocManager::install("ExperimentHub")
```

```{r warning=FALSE, message=FALSE}
library(ExperimentHub)
refreshHub(hubClass = "ExperimentHub")
ehub <- ExperimentHub()
myfiles <- query(ehub, "TransOmicsData")
myfiles
```

## Package installation

```{r warning=FALSE, message=FALSE}
# BiocManager::install("TransOmicsData")
```

To list the summarized metadata for all datasets in the package:

```{r warning=FALSE, message=FALSE}
library(TransOmicsData)
listDatasets()
```

## Citing `TransOmicsData`

We hope that `r Biocpkg("TransOmicsData")` will be useful for your research. Please use the following information to cite the package. Thank you!

```{r "citation"}
## Citation info
citation("TransOmicsData")
```

# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
options(width = 120)
sessionInfo()
```
